Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-03-07 manuscript.Rmd
ppt stats

## Participants

@@

#Worst three Kappa individuals are 9, 111-4, and 120-2
#Worst three Kappa groups are 9, 110-4
#Worst three Overall Accuracy (grouped) are 104-1, 106-1, 108-2 (first two are pt 2 outliers)

>>>>

## Participants and Design

```{r participants}
ppts <- read_csv("data/imu-compiled.csv") %>% 
  mutate(id_uni = factor(id*100+session),
         group = factor(ifelse(age <= 8, "Younger", "Older")))
num_younger <- ppts %>% filter(group == "Younger") %>% .$id %>% unique(.) %>% length(.)
num_older <-  ppts %>% filter(group == "Older") %>% .$id %>% unique(.) %>% length(.)
num_sessions <- ppts %>% group_by(group, id, session) %>% slice_head(n = 1) %>% count %>% group_by(group, id) %>% count
age <- ppts %>% group_by(group) %>% get_summary_stats(age) %>% column_to_rownames("group")
```

Infants were recruited in one of two age groups: Younger infants were 4-7 months and older infants were 11-14 months. Families were recruited through social media advertisements and from community events in Southern California. There were `r num_younger` infants in the 4-7 month group (X female) and `r num_older` in the 11-14 month group (X female). Only 1 of session was excluded due to a technical error---one of the four IMU sensors failed to record, resulting in an unusable recording. The ethnicity for infants was reported as X Hispanix/Latinx and X for not Hispanix/Latinx. Race was reported as X Caucasian, X Asian, X ~~~ and X others. Parents were compensated \$30 in cash for each visit they completed. The BLINDED Institutional Review Board reviewed and approved all procedures associated with the study. All participants gave their informed consent to participate.
<!-- TODO RACE ETHNICITY SEX -->

Most participants were tested in a single session (`r nrow(num_sessions %>% filter(n == 1))`), but `r nrow(num_sessions %>% filter(n > 1))` participants contributed between 2-4 sessions as part of an ongoing longitudinal study. Across the two age groups, we report data on a total of `r length(unique(ppts$id_uni))` sessions, with `r num_sessions %>% filter(group == "Younger") %>% pull(n) %>% sum` from younger infants and `r num_sessions %>% filter(group == "Older") %>% pull(n) %>% sum` from older infants. Across sessions, younger infants' age ranged from `r age["Younger","min"]` to `r age["Younger","max"]` (*M* = `r age["Younger","mean"]`) and older infants' age ranged from `r age["Older","min"]` to `r age["Older","max"]` (*M* = `r age["Older","mean"]`).

<!-- with X including permission for data to be shared on Databrary.  -->

@@

### 2023-03-07 manuscript.tex
ppt stats

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

>>>>

\hypertarget{participants-and-design}{%
\subsection{Participants and Design}\label{participants-and-design}}

Infants were recruited in one of two age groups: Younger infants were 4-7 months and older infants were 11-14 months. Families were recruited through social media advertisements and from community events in Southern California. There were 9 infants in the 4-7 month group (X female) and 14 in the 11-14 month group (X female). Only 1 of session was excluded due to a technical error---one of the four IMU sensors failed to record, resulting in an unusable recording. The ethnicity for infants was reported as X Hispanix/Latinx and X for not Hispanix/Latinx. Race was reported as X Caucasian, X Asian, X \textasciitilde\textasciitilde\textasciitilde{} and X others. Parents were compensated \$30 in cash for each visit they completed. The BLINDED Institutional Review Board reviewed and approved all procedures associated with the study. All participants gave their informed consent to participate.

Most participants were tested in a single session (17), but 6 participants contributed between 2-4 sessions as part of an ongoing longitudinal study. Across the two age groups, we report data on a total of 34 sessions, with 14 from younger infants and 20 from older infants. Across sessions, younger infants' age ranged from 3.84 to 7.16 (\emph{M} = 4.99) and older infants' age ranged from 10.74 to 14.23 (\emph{M} = 11.75).
